# Colophon {-}

This document is set in [EB Garamond](https://github.com/georgd/EB-Garamond), [Source Code Pro](https://github.com/adobe-fonts/source-code-pro/) and [Lato](http://www.latofonts.com/lato-free-fonts/). The body text is set at 11pt with $\familydefault$.

It was written in R Markdown and $\LaTeX$, and rendered into PDF using [bookdown](https://github.com/rstudio/bookdown).

This document was typeset using the XeTeX typesetting system and the University of Nebraska thesis class (`nuthesis.cls`). The template is maintained at <https://github.com/near-center-unl/UNL-thesisdown-template>.

This version of the thesis was generated on `r Sys.time()`. The repository is currently at this commit:

```{r echo = FALSE, eval = FALSE}
# I've set eval=FALSE to ensure Travis-CI can run
# if you're not using Travis-CI, then eval=TRUE will be fine
library(git2r)
if ( in_repository() ) {
       summary(commits()[[1]])
} else {
       message("We are not in a git repository")
}
```

The computational environment that was used to generate this version is as follows:

```{r echo = FALSE}
devtools::session_info()
```
